\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    allcolors=black
}

\pagestyle{empty}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{#1}}%
     \item[]
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{-0.5#1}}%
\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}

% and the actual content starts here
\begin{document}

\begin{center}
	{\Large \textbf{Jochen Stierberger}}\\
	Chicago, Illinois
	\vspace{0.05cm}
	\\
	(626) 709-0712 \hfill
	\href{mailto:jochen@stierberger.com}{jochen@stierberger.com} \hfill
	\href{https://github.com/strbrgr}{github.com/strbrgr} \hfill
	\href{https://linkedin.com/in/strbrgr}{linkedin.com/in/strbrgr}
\end{center}
\vspace{1em} % Add space of 1em between sections
%
%----------------------------------------------------------------------------------------
% Work Experience
%----------------------------------------------------------------------------------------
%
\hrule
\vspace{-1em}
\subsection*{\Large Experience}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em


  \item
	      \headerrow
	      {\textbf{nvisia}}
	      {\textbf{Chicago, IL}}
	      \headerrow
	      {\emph{Software Engineer}}
	      {\emph{Nov 2023 -- Present}}
	      \begin{itemize*}
	      	\item Stood up innovative IoT enterprise application within 6 months for numerous Fortune 500 companies to enhance operational uptime.
          \item Innovated real-time data visualization by introducing diverse graph components (e.g., line and bar charts) to our team, pioneering dynamic insights and empowering customers to optimize cost efficiency.
	      	\item Leveraged creative background to enhance UX and UI, resulting in a more aesthetically pleasing and user-friendly experience.
	      \end{itemize*}
	      \headerrow
	      {\emph{Software Developer}}
	      {\emph{Oct 2022 -- Nov 2023}}
	      \begin{itemize*}
          \item Initiated and executed the development of an internal tool that automated a labor-intensive manual process, thereby elevating the developer experience and delivering notable cost and effort savings.
          \item Improved component load speed by 2x by fixing API request attributes, eliminating unnecessary data retrieval. Overcame integration challenges within a larger refactor and reduced payload by 10-20kb for enhanced system efficiency.
          \item Quickly adapted to a new, opinionated framework, making significant contributions within the first week. Implemented impactful changes to the sidebar layout, showcasing adaptability and enhancing project aesthetics and functionality.
          \item Played a pivotal role in the development of multiple applications, facilitating communication among over 10 business stakeholders.
	      \end{itemize*}
		
	\item
	      \headerrow
	      {\textbf{100Devs}}
	      {\textbf{remote}}
	      \headerrow
	      {\emph{Software Engineer}}
	      {\emph{Jan 2022 -- Oct 2022}}
	      \begin{itemize*}
	      	\item Collaborated closely with designers to ensure seamless integration of design elements into app platforms.
	      	\item Presented and implemented valuable tradeoff suggestions to business stakeholders, contributing to informed decision-making processes.
	      	\item Developed applications tailored for small local businesses.
	      \end{itemize*}
	      	      
	\item
	      \headerrow
	      {\textbf{The Field Museum}}
	      {\textbf{Chicago, IL}}
	      \headerrow
	      {\emph{Studio Manager}}
	      {\emph{Jun 2021 -- Jan 2022}}
	      \begin{itemize*}
	      	\item Produced high-magnification photographs and 3D models to advance fossil preparation techniques and conducted specimen research.
	      	\item Developed marketing assets across various media channels.
	      \end{itemize*}
	      	      
\end{itemize}
\vspace{1em} % Add space of 1em between sections
%
%----------------------------------------------------------------------------------------
% Skills
%----------------------------------------------------------------------------------------
%
\hrule
\vspace{-1em}
\subsection*{\Large Skills}

\hyphenpenalty=1000
\begin{itemize}[leftmargin=1em,noitemsep]
	\item \textbf{Programming Languages:}
	      JavaScript, TypeScript, HTML, CSS, Swift
	\item \textbf{Technologies:}
	      React, Next.js, Tailwind CSS, Azure DevOps, ESLint
\end{itemize}
\vspace{1em} % Add space of 1em between sections
%
%----------------------------------------------------------------------------------------
% Education
%----------------------------------------------------------------------------------------
%
\hrule
\vspace{-1em}
\subsection*{\Large Education}

\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	      \headerrow
	      {\textbf{University of Art and Design}}
	      {\textbf{Offenbach, Germany}}
	      \headerrow
	      {\emph{MFA Design}}
	      {\emph{2019}}
	      
	      	      
\end{itemize}

\end{document}
